---
title: "Untitled"
author: "Brian"
date: "2/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r load data}
File = 'fijiDownload.RData'
load(File)
```
This is the practice inspired by one of my assignment about how to model a data whose response variable (y) is counting numbers. Given this infomation of response variable, I would like to use generalized linear regression with link function of Poisson.\
\
```{r head}
# explore data
head(fijiFull)
```
We want to predict how many children does a woman have given her age, ethnicity, education situation, and the living place.\
\
```{r data manipulation}
# First get rid of newly married women, and those who are not educated:
fijiSub = fiji[fiji$monthsSinceM > 0 & !is.na(fiji$literacy), ]
# make a offset and make it log-based:
fijiSub$logYrsSinceM = log(fijiSub$monthsSinceM/12)
# make 15-18 years old the reference group:
fijiSub$ageMarried = relevel(fijiSub$ageMarried, '15to18')
# make the woman in rural area the reference group:
fijiSub$urban = relevel(fijiSub$residence, 'rural')
```
\
```{r glm regression}
fijiGlm = glm(
children ~ offset(logYrsSinceM) + ageMarried + urban + literacy + ethnicity,
family = poisson (link = log), data = fijiSub)

summary(fijiGlm)
```
\
```{r confidence interval}
# make a 95% CI:
rate = cbind(est = fijiGlm$coefficients, confint(fijiGlm, level = 0.95))
```
```{r CI and table}
knitr::kable(cbind(summary(
  fijiRes)$coefficients,
  exp(rate)),
  digits = 2) 
```
\
Want to know if all the variables are useful, then fit another model and do a likelihood ratio test.\
\
```{r glm regression 2}
fijiGlm2 = glm(
  children ~ offset(logYrsSinceM) + ageMarried + urban + ethnicity,
  family = poisson(link = log), data = fijiSub)

summary(fijiGlm2)
```
\
```{r table_2}
# table 2
rate2 = cbind(est = fijiGlm2$coef, confint(fijiGlm2, level = 0.95))
knitr::kable(cbind(
  summary(fijiGlm2)$coef,
  exp(rate2)),
  digits=2)
```
\
Now make a LRT to compare:\
\
```{r LRT}
lmtest::lrtest(fijiGlm2, fijiGlm)
```
\
P-value is greater than 0.05 which means it is not significant, thus, literacy should not be considered as a useful variable thus it should be removed from the fitted regression model.

